Z-Resonance at LEP

### 2010-09-03 Z0-Publikation/tex/paper-template.tex

\setlength{\marginparwidth}{1cm}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
\begin{document}
\hugehead

@@

The standard model of elementary particles describes interactions of particles
by four fundamental forces. Two of them, the electric and the weak forces, can
be seen as one force, the electroweak force. Its gauge
bosons, which mediate the force between the two interacting particles, are the
photon as well as the W$^{\pm}$- and the $Z^0$-boson. At the
electron-positron-collider LEP at CERN the $Z^0$ has been seen for the first
time, which was possible because of the sufficient center of mass energy of this
collider experiment.

@@

In this case the hadronic calorimeter and the muon chamber are the most
important parts. The hadronic calo- rimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without a significant loss of energy, because these are the only particles that
are able to reach there.
% Further information about the detector design can be found in \cite{script}.

>>>>

\setlength{\marginparwidth}{1cm}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}

\hyphenation{calo-rimeter}

\begin{document}
\hugehead

@@

The standard model of elementary particles describes interactions of particles
by four fundamental forces. Two of them, the electric and the weak forces, can
be seen as one force, the electroweak force. Its gauge
bosons, which mediate the force between the two interacting particles, are the
photon as well as the $W^{\pm}$- and the $Z^0$-boson. At the
electron-positron-collider LEP at CERN the $Z^0$ has been seen for the first
time, which was possible because of the sufficient center of mass energy of this
collider experiment.

@@

In this case the hadronic calorimeter and the muon chamber are the most
important parts. The hadronic calorimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without a significant loss of energy, because these are the only particles that
are able to reach there.
% Further information about the detector design can be found in \cite{script}.
